Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-06-03 tex/VHzQ.tex
Added AM and ES acknowledgment

Critically, we now have available to us new W1 and W2 photometry from
the `unWISE Source Catalog' \citep[][]{Schlafly_Meisner2018}, a
WISE-selected catalogue that is based on significantly deeper imaging
and has a more extensive modeling of crowded regions than the ALLWISE
release. For the first time in a catalogue, unWISE takes advantage of
the ongoing mid-IR Near-Earth Object Wide-Field Infrared Survey
Explorer Reactivation mission \citep[NEOWISE-R; ][]{Mainzer2014}, and
achieves depths $\sim$0.7 mag deeper than ALLWISE (in W1/2).  This
additional depth is a significant advantage in the detection and study
of VH$z$Qs in the 3-5 micron regime.

@@

>>>>

Critically, we now have available to us new W1 and W2 photometry from the `unWISE Source Catalog' \citep[][]{Schlafly2019}, a WISE-selected catalogue that is based on significantly deeper imaging and has a more extensive modeling of crowded regions than the ALLWISE release. For the first time in a catalogue, unWISE takes advantage of the ongoing mid-IR Near-Earth Object Wide-Field Infrared Survey Explorer Reactivation mission \citep[NEOWISE-R; ][]{Mainzer2014}, and achieves depths $\sim$0.7 mag deeper than ALLWISE (in W1/2).  This additional depth is a significant advantage in the detection and study of VH$z$Qs in the 3-5 micron regime.

@@

We very much thank Aaron Meisner and Eddie Schlafly for facilitating early access to the unWISE Catalog.
